### 2021-11-09 Final Doc/Chapters/Chapter4.tex
Article Documentation Complete
Final Push

\section{Artefact}
The artefact that was developed is a computer game and is titled \textit{"Puzzle Ball: Spherical Shadows"} and is a self-contained application that can be launched standalone without any additional software needed. While it is fairly lightweight on hardware resources for a computer game, it does require more resources than a typical application and may stutter on older systems due to the effects used. In terms of the genres it encompass, it would full under the platformer, puzzle and action genres for games and as such is described as a 3D puzzle platformer with aspects of action gameplay played in first person.
\\\\
Once the application is launched, the user is taken to the \textit{Main Menu} screen (depicted below) where clicking the text \textit{Play} triggers a function to start the first level - that being the the Tutorial. Each group member was responsible for the design of an individual level where the Tutorial/First level being the level undertaken in this project. The reason for this is that the research aspect of this project aligns with the goals of a tutorial level.

@@

\noindent One the tutorial level has started, the user is shown the basic character movement controls on the right side of the screen and can continue forward. Text based signs were used throughout the level to explain various mechanics or tasks to be completed - an example of this is shown in Figure 4.2 below.

@@

\noindent The user must then make there way to a central area, referred to as the Hub Room, where they are given the choice in what order they would like to complete the five main tutorials. These will be discussed and shown below. As the user completes the several tutorials, a blockade that restricted movement to the next level is slowly removed as shown below.

\begin{figure}[H]
\centering
\begin{subfigure}{0.3\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/barrier5.png}
  \caption{No Tutorials Completed}
\end{subfigure}%
\begin{subfigure}{0.3\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/barrier3.png}
  \caption{Two Tutorials Completed}
\end{subfigure}
\begin{subfigure}{0.3\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/barrier0.png}
  \caption{All Tutorials Completed}
\end{subfigure}
\caption{Progress Blocker in Tutorial}
\end{figure}

@@

\noindent Once the ball object collides with the end goal object, the user is taken to the next level where the main aim to to traverse the level and throw the ball object into the next end goal. This process is followed for two additional levels for three in total  after which the user is taken to a scene where the group members and their contributions are listed with a prompt to close the application.

@@

\noindent A list of all assets made use of during the development of the artefact, such as models and music, can be found on the GitHub repositories\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows/blob/main/References.txt}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/References.txt}} 
\section{Article}
The individual research aspect of this project yielded a academic article titled \textit{"Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains"}.
\\\\
A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?} This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
\\\\
The results of the research aspect of this project is the answer to these questions which were synthesised from various case studies and the literature analysis conducted. The literature study of the article is similar to the one conducted in this document with the addition to an analysis of three case studies in detail, one of which was mentioned in the literature study above in Chapter \ref{Chapter2}.
\\\\
The three case studies made use of are all titled:
\begin{itemize}
\item \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"}
\item \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"}
\item \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"}
\end{itemize}

@@

\noindent In addition to these, qualities were derived from several educational theories discussed in the literature study as well as the findings section of the article. These include Merrill's First Principles, the ARCS model for motivation and a framework specific to teaching preschool children.
\\\\
The results of this encompass four archetypal qualities needed as well as a few qualities recommendations needed to be taken into account depending on the knowledge domain a topic falls under. The reasoning for choosing these specific qualities and recommendations is elaborated in detail in the article itself which can be found in Appendix \ref{AppendixC}. In short these qualities are named:
\begin{enumerate}
\item Reflection
\item Feedback
\item Story-telling
\item Structuring
\end{enumerate}

\noindent Reflection is described and giving a user enough time after they have completed a task or presented with new knowledge to think about it on their own without further instruction.
\\\\
The next quality is Feedback. Users should be given feedback on how they are progressing on a given set of tasks within the game at some point. Feedback should also be scaled up or down depending on how a user is progressing - that is, if a user is doing well they require less feedback on where to improve as compared to another user who may be struggling and should require more feedback on how to improve. Further than this, the means of presenting feedback is heavily dependant on the topic being taught, how tasks are handles and the general loop of the game. In addition to this. Feedback also includes the stipulation that the game should foster an environment of smaller accomplishments to keep users engaged with the game.
\\\\
Story-telling is also an important quality which centres around keeping engagement with the game high. It entails making use a story or role-play within the game or the use of a story-based agent such as a character that would guide users through the material and tasks. This can be done through contextual story-telling by having the tasks form part of a story's progression or as the main means of relaying information on a topic.
\\\\
The next quality encompasses a major part of the design of the game. Structuring refers to both the overall design of a serious game as well as how the tasks within it are designed. This quality has several key requirements that should be met for the most optimal experience by a user. Goals and expectations should be made simple and clear to a user from the beginning. Tasks and problems within the game should also scale in difficulty depending on a user's skill and progression - that is, when a user is struggling the tasks should be made easier until they demonstrate understanding with them upon which the difficulty is increased. A serious game in this context should also be designed around the topic making the information or tasks and problems the main focus of the game.
\\\\
While the above qualities are intended for use in any serious game being developed, the following section details certain recommendations for various knowledge domains. The definitions for each of these was also given in the literature study in Chapter \ref{Chapter2}.
\\\\
Both Hi-fidelity and low fidelity simulation games, these being a subset of serious games, are the most useful for teaching content found in the Affective, Soft Skills and Psychomotor domains since the best means to teach these is through immersing the user in the phenomena, repeated application of skills and observation respectively. Simulation-type serious games can also be used in the other domains such as with the game used to aid in teaching physics. These types of games are also the most effective means for the Psychomotor domain.
\newpage
\noindent The remaining knowledge domains tend to have some heavy overlap depending on the topic being covered. The Conceptual-Procedural principle is an example of this. To reiterate, it simply states that a topic cannot be fully understood from only the procedures or context - both are needed for a deeper understanding. As such if a topic where to fall under these domains it is vital to present information in a manner that all aspects are clear to a user.

\section{Conclusion}
This section dealt with the results generated as part of this research project. This included a digital computer game as well as various qualities needed in order for a serious game to be effectively used in an educational environment. In brief, these qualities were, Reflection, Feedback, Structuring and Story-telling.

>>>>

\section{Artefact}
The artefact that was developed is a computer game and is titled \textit{"Puzzle Ball: Spherical Shadows"} and is a self-contained application that can be launched standalone without any additional software needed. While it is fairly lightweight on hardware resources for a computer game, it does require more resources than a typical application and may stutter on older systems due to the effects used. In terms of the genres it encompasses, it would fall under the platformer, puzzle and action genres for games and as such is described as a 3D puzzle platformer with aspects of action gameplay played in the first person.
\\\\
Once the application is launched, the user is taken to the \textit{Main Menu} screen (depicted below) where clicking the text \textit{Play} triggers a function to start the first level - that being the Tutorial. Each group member was responsible for the design of an individual level where the Tutorial/First level being the level undertaken in this project. The reason for this is that the research aspect of this project aligns with the goals of a tutorial level.

@@

\noindent Once the tutorial level has started, the user is shown the basic character movement controls on the right side of the screen and can continue forward. Text-based signs were used throughout the level to explain various mechanics or tasks to be completed - an example of this is shown in Figure 4.2 below.

@@

\noindent The user must then make their way to a central area referred to as the Hub Room, where they are given the choice in what order they would like to complete the five main tutorials. These will be discussed and shown below. As the user completes the several tutorials, a blockade that restricted movement to the next level is slowly removed as shown below.

\begin{figure}[H]
\centering
\begin{subfigure}{0.3\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/barrier5.png}
  \caption{No Tutorials Completed}
\end{subfigure}%
\begin{subfigure}{0.3\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/barrier3.png}
  \caption{Two Tutorials Completed}
\end{subfigure}
\begin{subfigure}{0.3\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/barrier0.png}
  \caption{All Tutorials Completed}
\end{subfigure}
\caption{Progress Blocker in Tutorial}
\end{figure}

@@

\noindent Once the ball object collides with the end goal object, the user is taken to the next level where the main aim is to traverse the level and throw the ball object into the next end goal. This process is followed for two additional levels for three in total after which the user is taken to a scene where the group members and their contributions are listed with a prompt to close the application.

@@

\noindent A list of all assets made use of during the development of the artefact, such as models and music, can be found on the GitHub repositories\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows/blob/main/References.txt}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/References.txt}} 
\section{Article}
The individual research aspect of this project yielded an academic article titled \textit{"Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains"}.
\\\\
A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?} This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
\\\\
The results of the research aspect of this project are the answer to these questions which were synthesised from various case studies and the literature analysis conducted. The literature study of the article is similar to the one conducted in this document with the addition to an analysis of three case studies in detail, one of which was mentioned in the literature study above in Chapter \ref{Chapter2}.
\\\\
The three case studies made use of are all titled:
\begin{itemize}
\item \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"}
\item \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"}
\item \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"}
\end{itemize}

@@

\noindent In addition to these, qualities were derived from several educational theories discussed in the literature study as well as the findings section of the article. These include Merrill's First Principles, the ARCS model for motivation and a framework specific to teaching preschool children.
\\\\
The results of this encompass four archetypal qualities needed as well as a few qualities recommendations that needed to be taken into account depending on the knowledge domain a topic falls under. The reasoning for choosing these specific qualities and recommendations is elaborated in detail in the article itself which can be found in Appendix \ref{AppendixC}. In short, these qualities are named:
\begin{enumerate}
\item Reflection
\item Feedback
\item Story-telling
\item Structuring
\end{enumerate}

\noindent Reflection is described and giving a user enough time after they have completed a task or presented with new knowledge to think about it on their own without further instruction.
\\\\
The next quality is Feedback. Users should be given feedback on how they are progressing on a given set of tasks within the game at some point. Feedback should also be scaled up or down depending on how a user is progressing - that is, if a user is doing well they require less feedback on where to improve as compared to another user who may be struggling and should require more feedback on how to improve. Further than this, the means of presenting feedback is heavily dependant on the topic being taught, how tasks are handled and the general loop of the game. In addition to this. Feedback also includes the stipulation that the game should foster an environment of smaller accomplishments to keep users engaged with the game.
\\\\
Story-telling is also an important quality that centres around keeping engagement with the game at a high level. It entails making use of a story or role-play within the game or the use of a story-based agent such as a character that would guide users through the material and tasks. This can be done through contextual story-telling by having the tasks form part of a story's progression or as the main means of relaying information on a topic.
\\\\
The next quality encompasses a major part of the design of the game. Structuring refers to both the overall design of a serious game as well as how the tasks within it are designed. This quality has several key requirements that should be met for the most optimal experience by a user. Goals and expectations should be made simple and clear to a user from the beginning. Tasks and problems within the game should also scale in difficulty depending on a user's skill and progression - that is, when a user is struggling the tasks should be made easier until they demonstrate understanding with them upon which the difficulty is increased. A serious game in this context should also be designed around the topic making the information or tasks and problems the main focus of the game.
\\\\
While the above qualities are intended for use in any serious game being developed, the following section details certain recommendations for various knowledge domains. The definitions for each of these was also given in the literature study in Chapter \ref{Chapter2}.
\\\\
Both Hi-fidelity and low fidelity simulation games, these being a subset of serious games, are the most useful for teaching content found in the Affective, Soft Skills and Psychomotor domains since the best means to teach these is through immersing the user in the phenomena, repeated application of skills and observation respectively. Simulation-type serious games can also be used in other domains such as with the game used to aid in teaching physics. These types of games are also the most effective means for the Psychomotor domain.
\newpage
\noindent The remaining knowledge domains tend to have some heavy overlap depending on the topic being covered. The Conceptual-Procedural principle is an example of this. To reiterate, it simply states that a topic cannot be fully understood from only the procedures or context - both are needed for a deeper understanding. As such if a topic were to fall under these domains it is vital to present information in a manner that all aspects are clear to a user.

\section{Conclusion}
This section dealt with the results generated as part of this research project. This included a digital computer game as well as various qualities needed in order for a serious game to be effectively used in an educational environment. In brief, these qualities were Reflection, Feedback, Structuring and Story-telling.

### 2021-11-09 Final Doc/Chapters/Chapter5.tex
Final Push

\section{What was Learnt Throughout this Project}
In terms of what was learnt during the duration of this project, there were several new technologies and software in addition to a vast amount of knowledge from various fields.
\\\\
On the software side of things, the largest one was the Unity Editor, specifically the 2019.4.22f build of it, which was the main tool in developing the artefact. The choice of using Unity over another game engine, such as Unreal or Godot, was mainly due to the programming language it used (that being C\#). This was the language that most of the group, excluding myself, was familiar with and most experienced with when compared to the alternatives. Following this, C\# was also a new language learnt for this project and while the initial usage of it was difficult, with the experience  Java, another object-oriented language, it became easy to write and implement the scripts needed. 
\\\\
Another technology made use of, and consequently learnt, is GitHub. This was used for version control and was the simplest way to handle it. The GitHub Desktop application was used for facilitating this. 
\\\\
\LaTeX was another technology used in the latter half the project. It is a software tool that allows for the creation of PDF's and was used for the Article as well as the final documentation. While it was initially hard to pick up and use, it also became easier with time. It allowed for these respective documents to be presented very neatly and should have been used earlier on in the project's development. 
\\
A fair amount of information concerning game design was also learnt form how psychology plays a factor in the choices game designers take when developing a game or user interface. While a fair amount of this knowledge was used when designing the artefact, there is still much more that could have been incorporated - such as the aforementioned use of psychology to style the game better.
\\\\
Additionally, various knowledge in the fields used for the research article was learnt. These were fields concerning educational and instructional theories, the study of games as well as turning tasks into some form of game be it digital or not. These topics were interesting to examine and read about and were a tremendous help on how to approach any future educational endeavours such as tutoring. 
\\\\
As this project was described to be under \textit{Entertainment Computing}, being able to analyse other computer games was vital to garner a proper understanding of how to go about the development of both the artefact and article. This process was heavily aided by Prof. Günther Drevin where we were tasked with various presentations on the field of ludology itself and on the analysis of a game - Myst.

\section{Development of Artefact}
The primary aim of this study was stated as, \textit{to identify what qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information.}

@@

\noindent The artefact was successfully developed meaning the overall aim was indeed also met. While the first two objectives set were also met in full the last objective was only met in part. The artefact and research aspects of this project are distinct with no correlation between each other bar the main topic at hand being \textit{Entertainment Computing} and this aim sought to combine them. The research was focused on educational games and the level designed was the tutorial level which intends to teach players and as such there is a correlation. The qualities identified by the research study were implemented, such as with Reflection being done by giving the user time after each section before continuing to the next. However, the objective stated the use of both audio and visual stimuli where the final implementation of the artefact makes use of only visual. While this is a small distinction to make on a self-imposed objective, it would have been a fine inclusion to make which would have also aided users who struggle with reading.
\\\\
Another aspect of the artefact and article development to discuss is the tame management of it all. While all milestone submissions were delivered on time, the time management of the individual aspects of the project were lacking. The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation, were only finalised a few days prior to the deadlines with final checks typically happing on the day of submission. As such, individual time management on this project was lacking, especially nearing deadlines while the group aspects were handled especially well - even when issues in development arose.
\\\\
Following on from that point, the group aspects of this project were exceptionally well handled. As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development. These were: %itemise and itemise again
\begin{table}[H]
\begin{tabular}{l|l|l}
\hline
Joshua Esterhuizen       & GC Wehmeyer          & Rickus Trollip           \\ \hline
Player Movement          & Player Animation     & Main Menu                \\
Ball physics             & Health Bar           & Enemy AI                 \\
Moving platforms         & Player Model         & Game music aquisition    \\
Portal asset development & Enemy Models         & Controller configuration \\
Teleportation            & Environment assets   & Second Level designer    \\
Pause Menu               & Third Level designer &                          \\
Level Transition         &                      &                          \\
Tutorial level designer  &                      &                          \\ \hline
\end{tabular}
\end{table}

\noindent As indicated in the lists above, there was a roughly equal contribution from each group member. There was also no major problems with group dynamics throughout the duration of this project as each member was respectful and eager to learn about the aspects which the others were responsible for. 
\\\\
The only notable incident during development was an issue with the standalone build where certain script references were not working when they did while in the editor. While this issue was a stressful issue as it concerned a cornerstone of the game, it was resolved after a few hours debugging of the issue.

\section{Future Work Possibilities}
While the project is considered to completed as it stands, there are still aspects that can be improved or others added. In terms of the artefact, there are numerous game design techniques that could still be taken advantage of. One example of this is Culling. This is a process by which certain elements within a game are unloaded and removed while the user is not viewing or interacting with them. The Unity Editor does include a simple version of this, however, a more robust means of it could be implemented with additional research into the feature. 
\\\\
With respect to the research study and article, there are two possibilities for future work. One is to simply continue the research and expand on what was already found and including additional fields to perhaps describe new qualities. For a more practical approach, an actual serious game could be designed and developed once a suitable topic is found to present in this format.

\section{Conclusion}
The process of working through a project in this capacity was an exciting learning experience. Being able to work on a topic that has always been a personal interest was an immense help to keep the motivation of working on both an individual research assignment and a group artefact at an all time high. The process of creating a provisional plan, performing literary research and documenting the entire development process was certainly a new way of approaching a project for myself. This way of completing a project is certainly a major help to finishing the project while maintaining the original aim and scope at all times. It was certainly a valuable educational and personal experience which will be useful in all future projects I take part in.

>>>>

\section{What was Learnt Throughout this Project}
In terms of what was learnt during the duration of this project, there were several new technologies and software in addition to a vast amount of knowledge from various fields.
\\\\
On the software side of things, the largest one was the Unity Editor, specifically the 2019.4.22f build of it, which was the main tool in developing the artefact. The choice of using Unity over another game engine, such as Unreal or Godot, was mainly due to the programming language it used (that being C\#). This was the language that most of the group, excluding myself, was familiar with and most experienced with when compared to the alternatives. Following this, C\# was also a new language learnt for this project and while the initial usage of it was difficult, with experience in Java, another object-oriented language, it became easy to write and implement the scripts needed. 
\\\\
Another technology made use of, and consequently learnt, is GitHub. This was used for version control and was the simplest way to handle it. The GitHub Desktop application was used for facilitating this. 
\\\\
\LaTeX was another technology used in the latter half of the project. It is a software tool that allows for the creation of PDF's and was used for the Article as well as the final documentation. While it was initially hard to pick up and use, it also became easier with time. It allowed for these respective documents to be presented very neatly and should have been used earlier on in the project's development. 
\\
A fair amount of information concerning game design was also learnt from how psychology plays a factor in the choices game designers take when developing a game or user interface. While a fair amount of this knowledge was used when designing the artefact, there is still much more that could have been incorporated - such as the aforementioned use of psychology to style the game better.
\\\\
Additionally, various knowledge in the fields used for the research article was learnt. These were fields concerning educational and instructional theories, the study of games as well as turning tasks into some form of a game be it digital or not. These topics were interesting to examine and read about and were a tremendous help on how to approach any future educational endeavours such as tutoring. 
\\\\
As this project was described to be under \textit{Entertainment Computing}, being able to analyse other computer games was vital to garner a proper understanding of how to go about the development of both the artefact and article. This process was heavily aided by Prof. Günther Drevin where we were tasked with various presentations on the field of ludology itself and the analysis of a game - Myst.

\section{Development of Artefact}
The primary aim of this study was stated as \textit{to identify what qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information.}

@@

\noindent The artefact was successfully developed meaning the overall aim was indeed also met. While the first two objectives set were also met in full the last objective was only met in part. The artefact and research aspects of this project are distinct with no correlation between each other bar the main topic at hand being \textit{Entertainment Computing} and this aim sought to combine them. The research was focused on educational games and the level designed was the tutorial level which intends to teach players and as such, there is a correlation. The qualities identified by the research study were implemented, such as with Reflection being done by giving the user time after each section before continuing to the next. However, the objective stated the use of both audio and visual stimuli where the final implementation of the artefact makes use of only visuals. While this is a small distinction to make on a self-imposed objective, it would have been a fine inclusion to make which would have also aided users who struggle with reading.
\\\\
Another aspect of the artefact and article development to discuss is the tame management of it all. While all milestone submissions were delivered on time, the time management of the individual aspects of the project was lacking. The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation, were only finalised a few days prior to the deadlines with final checks typically happing on the day of submission. As such, individual time management on this project was lacking, especially nearing deadlines while the group aspects were handled especially well - even when issues in development arose.
\\\\
Following on from that point, the group aspects of this project were exceptionally well handled. As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development. These were: %itemise and itemise again
\begin{table}[H]
\begin{tabular}{l|l|l}
\hline
Joshua Esterhuizen       & GC Wehmeyer          & Rickus Trollip           \\ \hline
Player Movement          & Player Animation     & Main Menu                \\
Ball physics             & Health Bar           & Enemy AI                 \\
Moving platforms         & Player Model         & Game music aquisition    \\
Portal asset development & Enemy Models         & Controller configuration \\
Teleportation            & Environment assets   & Second Level designer    \\
Pause Menu               & Third Level designer &                          \\
Level Transition         &                      &                          \\
Tutorial level designer  &                      &                          \\ \hline
\end{tabular}
\end{table}

\noindent As indicated in the lists above, there was a roughly equal contribution from each group member. There was also no major problems with group dynamics throughout the duration of this project as each member was respectful and eager to learn about the aspects for which the others were responsible. 
\\\\
The only notable incident during development was an issue with the standalone build where certain script references were not working when they did while in the editor. While this issue was a stressful issue as it concerned a cornerstone of the game, it was resolved after a few hours debugging of the issue.

\section{Future Work Possibilities}
While the project is considered to be completed as it stands, there are still aspects that can be improved or others added. In terms of the artefact, numerous game design techniques could still be taken advantage of. One example of this is Culling. This is a process by which certain elements within a game are unloaded and removed while the user is not viewing or interacting with them. The Unity Editor does include a simple version of this, however, a more robust means of it could be implemented with additional research into the feature. 
\\\\
With respect to the research study and article, there are two possibilities for future work. One is to simply continue the research and expand on what was already found and include additional fields to perhaps describe new qualities. For a more practical approach, an actual serious game could be designed and developed once a suitable topic is found to present in this format.

\section{Conclusion}
The process of working through a project in this capacity was an exciting learning experience. Being able to work on a topic that has always been a personal interest was an immense help to keep the motivation of working on both an individual research assignment and a group artefact at an all-time high. The process of creating a provisional plan, performing literary research and documenting the entire development process was certainly a new way of approaching a project for myself. This way of completing a project is certainly a major help to finishing the project while maintaining the original aim and scope at all times. It was certainly a valuable educational and personal experience that will be useful in all future projects I take part in.
